Object-Oriented Internet - Azure interoperability

### 2020-09-29 Latex/Manuscript..tex
md conversion to latex #24
- fixes #24

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\date{}

@@

@@

>>>>

\documentclass{article}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}

\providecommand{\tightlist} { \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\title{Object-Oriented Internet - Azure interoperability} 
\author[1]{Mariusz Postół}
\author[2]{Piotr Szymczak}
\author[3]{Clemens Vasters}
\affil[1, 2]{Institute of Information Technology, Lodz University of Technology, Łódź, Poland}
% \email{mailto:mariusz.postol@p.lodz.pl} 
\affil[3]{Microsort}
%\tocauthor{Mariusz Postół}
%\institute{ Institute of Information Technology, Lodz University of Technology, Łódź, Poland \email{mailto:mariusz.postol@p.lodz.pl} }

@@

\maketitle

\begin{abstract}

  Information and Communication Technology has provided society with a~vast variety of distributed applications. By design, the deployment of this kind of application has to focus primarily on communication. This article addresses research results on the systematic approach to the design of the meaningful Machine to Machine (M2M) communication targeting distributed mobile applications in the context of new emerging disciplines, i.e. Industry 4.0 and Internet of Things. This paper contributes to the design of a new architecture of mobile IoT solutions designed atop of the M2M communication and composed as multi-vendor cyber-physicals systems. The described reusable library supporting this architecture designed using the reactive interoperability archetype proves that the concept enables a systematic approach to the development and deployment of software applications against mobile IoT solutions based on international standards. Dependency injection and adaptive programming engineering techniques have been engaged to develop a full-featured reference application program and make the proposed solution scalable and robust against deployment environment continuous modifications. The article presents an executive summary of the proof of concept and describes selected conceptual and experimental results achieved as an outcome of the open-source project Object-Oriented Internet targeting multi-vendor plug-and-produce interoperability scenario.

%\keywords{Industrial communication \and Industry 4.0 \and Internet of Things \and Machine to Machine Communication \and OPC Unified Architecture}

\end{abstract}

\maketitle

@@

\bibliography{Manuscript}
\bibliographystyle{splncs04}
